\section*{Data Preprocessing}
\subsection*{What preprocessing/cleaning was done? (\eg discretization or bucketing, tokenization, part-of-speech tagging, SIFT feature extraction, removal of instancess, processing of missing values)?}
% \texttt{If so, please provide a description. If not, you may skip the remainder of the questions in this section.}}
\noindent The following steps were taken to process the data:
\begin{enumerate}

\item \emph{Gathering raw images} First the raw images for this
dataset were obtained from the Faces in the Wild dataset
consisting of images and associated captions gathered from
news articles found on the web.
2. Running the Viola-Jones face detector4 The OpenCV version 1.0.0 release 1 implementation of Viola-Jones face detector was used to detect faces in each of these images, using
the function cvHaarDetectObjects, with the provided Haar
classifier—cascadehaarcascadefrontalfacedefault.xml. The
scale factor was set to 1.2, min neighbors was set to 2, and
the flag was set to CV HAAR DO CANNY PRUNING.
3. Manually eliminating false positives: If a face was detected and the specified region was determined not to be a
face (by the operator), or the name of the person with the
detected face could not be identified (using step 5 below),
the face was omitted from the dataset.
4. Eliminating duplicate images: If images were determined
to have a common original source photograph, they are defined to be duplicates of each other. An attempt was made to
remove all duplicates but a very small number (that were not
initially found) might still exist in the dataset. The number
of remaining duplicates should be small enough so as not
to significantly impact training/testing. The dataset contains
distinct images that are not defined to be duplicates but are
extremely similar. For example, there are pictures of celebrities that appear to be taken almost at the same time by different photographers from slightly different angles. These
images were not removed.
5. Labeling (naming) the detected people: The name associated with each person was extracted from the associated
\end{enumerate}

\subsection*{Was the “raw” data saved in addition to the preprocessed/cleaned data? (\eg to support unanticipated future uses)}
\noindent
\subsection*{Is the preprocessing software available?}
\noindent
\subsection*{Does this dataset collection/processing procedure achieve the motivation for creating the dataset stated in the first section of this datasheet? If not, what are the limitations?}
\noindent
