\section*{Uses}
\subsection*{What (other) tasks could the dataset be used for?}
\noindent Family classification, large scale search \& retrieval, fine-grained categorization, tri-subject verification, hierarchical clustering, to name a few.


\subsection*{Has the dataset been used for any tasks already? \texttt{If so, where are the results so others can compare (\eg links to published papers)?}}
\noindent 
\subsection*{Has the dataset been used for any tasks already? \texttt{If so, please provide a description.}}
Papers using this dataset and the specified evaluation protocol are
listed in http://vis-www.cs.umass.edu/lfw/results.html
\subsection*{Is there a repository that links to any or all papers or systems that use the dataset?}
%  If so, please provide a link or other access point.
Papers using this dataset and the specified training/evaluation
protocols are listed under “Methods” section of http://vis-www.cs.
umass.edu/lfw/results.html


\subsection*{What (other) tasks could the dataset be used for?}
The LFW dataset can be used for the face identification problem.
Some researchers have developed protocols to use the images in
the LFW dataset for face identification.5


\subsection*{Is there anything about the composition of the dataset or the way it was collected and preprocessed/cleaned/labeled that might impact future uses?}
% For example, is there anything that a future user might need to know to avoid uses that could result in unfair treatment of individuals or groups (\eg stereotyping, quality of service issues) or other undesirable harms (\eg financial harms, legal risks) If so, please provide a description. Is there anything a future user could do to mitigate these undesirable harms?

There is minimal risk for harm: the data was already public.
\subsection*{Are there tasks for which the dataset should not be used?}
% \texttt{If so, please provide a description.The dataset should not be used for tasks that are high stakes (e.g. law enforcement).}
\subsection*{Any other comments?}
